---
title: "Week 3: Agriculture, Industrialization & Global Trade" 
author: | 
    | Dr. Gabriel Geisler Mesevage 
    | gabriel.mesevage@kcl.ac.uk
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  xaringan::moon_reader:
    nature:
      beforeInit: "helper_functions/macros.js"
      ratio: '16:9'
    lib_dir: libs
    css: ["xaringan-themer.css", "helper_functions/extra.css"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE,
                      message = FALSE, fig.align='center', fig.retina=3,
                      out.width="75%")
```

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
style_solarized_light()
source("helper_functions/theme_lecture.R")
xaringanExtra::use_webcam()
xaringanExtra::use_tile_view()
```


## Today's Goals

.Large[
1. The revolution in *agriculture*

  + It predates the industrial revolution
  + Persists throughout the industrial revolution
  + Mostly what people do even long after the industrial revolution!


2. The impact of the industrial revolution on *global patterns of economic production*

]

---

.Large[
## Today's Plan

1. The state of agriculture in the 18th century
2. The form and spread of industrialization
3. Industrial production in global trade
4. Global specialization and its consequences
5. Conclusion: the costs of not industrializing?
]

---

+ Stuff from Federico and Osterhammel

---

+ Decline of famines

---

+ geographic and ag system range e.g. rice vs wheat

---

+ The spread of industrialization

--- 

+ Some geographic range

---

+ The rise of trade

+ Maybe europe and hungry 40s first?

---

+ Trade and specialization

---

+ Specialization/grain invasion range of geographical and political effects

---

+ engels law the question of global development


